Word Sense Disambiguation: Pipelining with Supervised LSA

### 2014-05-11 paper.tex
some added citations

	Need to get list of papers and cite them in text as well. These are on the Google Doc and also in Kiran's Chrome tabs. Also we all have the book Albert sent out.

>>>>

	1. Agirre, Eneko, and Philip Glenny. Edmonds. Word Sense Disambiguation: Algorithms and Applications. Dordrecht: Springer, 2006. Print.

	2. Phil Katz and Paul Goldsmith-Pinkham. 2006. Word Sense Disambiguation Using Latent Semantic Analysis. 
	   Retrieved from http://www.sccs.swarthmore.edu/users/07 /pkatz1/cs65f06-final.pdf.

	3. T.K. Landauer, Foltz P.W., and D. Laham. 1998. Introduction to latent semantic analysis. $\textit{Discourse Processes}$, $25:259-284$.
